Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/example.tex
edited the qrr

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide}, answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the input and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question.  In addition, the QRR has categorized a generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

>>>>

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide}, answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the natural language question, namely the input and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question.  In addition, the QRR has categorized a generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

### 2010-03-05 paper/semsearch10/content/qrr.tex
edited the qrr

Conceptually, a QRM is the data structure that models the question answering process.  All QRMs are associated with a SSQ set of possible input categories and also output catgories.  It contains representations for every page visited and the order of visitation.  For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlight portions of the webpage).

The ontologcal representation of the SSQ is described in section {{XXX}}.  The following is a mathematical description of the information collected for user web interactions.

A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:

>>>>

Conceptually, a QRM is the data structure that models the question answering process.  Each QRMs contains an ontilogical realm, an SSQ, and information to support the query answering process.  The realm may be one or more descriptive categories and is used for is used for classification of the QRMs.  The SSQ describes the set of possible input categories and also output catgories from the associated natural language query.  The possible set of input phrase inputs and outputs are grouped in to contextual bins labeled \emph{who}, \emph{what}, \emph{when} and \emph{where}.  The ontilogical realm and the SSQ parameters act as a signature for the the QRM object, analogous to a function signature.   The ontologcal representation of the SSQ is described in section {{XXX}}.

Additionally, the QRM contains representations for every page visited and the order of visitation.  For each page, we store the list of inputs to the URL such as form inputs and the possible outputs (highlight portions of the webpage).  There is a mapping between the SSQ the possible inputs user inputs or outputs used on any page to the specific page input.  Finally, there is a structure with mappings to the user inputs or outputs that are displayed to the user as answers.

The following is a mathematical description of the information collected for user web interactions.

A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ \footnote{It is important to not that both $\Upsilon$ and $\Omega$ make up the SSQ structure.} such that:
